---
title: "p8105_hw1_xl3495"
output: github_document
author: "Xueting Li"
---

# Problem 1
## Load dataset and the necessary library
```{r}
data("penguins", package = "palmerpenguins")
library(tidyverse)
```


## Dataset description

```{r}
row = nrow(penguins)
col = ncol(penguins)
flipper_length = penguins %>% pull(flipper_length_mm)
mean_flipper_length = mean(flipper_length,na.rm = TRUE)
```

The `penguins` dataset has 8 variables in total and the size of the dataset is `r row * col` (_nrow_:`r row`; _ncol_:`r col`). The variables basically describes features of penguins such as `species`(Adélie, Chinstrap and Gentoo), `body_mass`, `sex`(male/female) and `year`. Also, variables like `bill_length_mm` and `bill_depth_mm` describes the bill length and depth in millimeters separately. The variable `flipper_length_mm` is an integer denoting flipper length in millimeters, with `r mean_flipper_length`mm in average.

## The scatterplot of `flipper_length_mm (y)` vs `bill_length_mm (x)`:

```{r warning = FALSE}
#create a scatteplot
plot = ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species))+geom_point()
# Save as a JPEG
ggsave("scatter_plot.jpeg", plot = plot)
```
```{r echo = FALSE,warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species))+geom_point()
```

# Problem 2

## Create a dataframe
```{r}
#library(tidyverse) already loaded
df = tibble(
  norm_samp = rnorm(10),
  vec_logical = norm_samp > 0,
  vec_char = c("apples",
               "bananas",
               "chocolates",
               "daikon radish",
               "eggplant",
               "fudge",
               "grapes",
               "honeydew_melon",
               "ice_cream",
               "jicama"),
  vec_factor = factor(c("fruit",
                        "fruit",
                        "snack",
                        "vegetable",
                        "vegetable",
                        "snack",
                        "fruit",
                        "fruit",
                        "snack",
                        "vegetable"
                        ))
)

```
The dataframe looks like:
```{r echo = FALSE}
df
```

